The Splashback Radius of Planck-SZ clusters

### 2018-11-15 Paper_new/RSP_paper_new.tex
Added graphs in appendix and made some changes to appendix D

\section{Estimating the contamination of the blue galaxy population}
\label{sec:Errors}
{\bf Add figures to this appendix}.

To infer the color cut to separate star forming galaxies from the
quenched galaxy population, we cross-matched the SDSS spectroscopic
sample to its Pan-STARRS photometry. In Figure~\ref{xx}, we show the
plot of the Pan-STARRS $(g-r)$ color as a function of redshift, and
the color cut we use in our analysis. The SDSS spectroscopic sample is
however quite shallow, and thus consists of galaxies that are brighter
than the Pan-STARRS galaxies that we wish to cross-correlate. At
fainter magnitudes, we can expect photometric errors to scatter red
galaxies into the blue population, potentially contaminating the
correlation function measurement. This could erroneously cause for the
splashback feature observed in the blue population. Therefore, we
need to assess the possiblity of such a contamination.

In Figure~\ref{}, we show the photometric errors of the Pan-STARRS
galaxies as a function of magnitude in each of the bands we use. The
galaxies that we use in our cross-correlation for the red/blue
analysis have an absolute magnitude of $M_{i}-5\log h=-18.94$. This
corresponds to a different apparent magnitude limit at each redshift.
For each spectroscopically matched galaxy, we figure out how faint the
apparent magnitude limit in the $i$ band is compared to the actual
apparent magnitude of the galaxy. We assume that the populations of
galaxies that we use to cross-correlate with clusters have the same
intrinsic colors, but are just fainter. This gives us the true
intrinsic magnitude of the galaxies that we cross-correlate in the
$g$ and the $r$ band. We perturb these magnitudes by the expected
errors at that magnitude as seen in Figure~\ref{}.

Next, we compute the fraction of galaxies which were intrinsically red
that now enter the blue population as defined using the same color
cut, but based on the perturbed magnitudes as a result of photometric
errors. We find such contamination of intrinsically red galaxies to
the blue population to be about 5 percent. This value would apply in
the field. Given that the red fraction is higher in clusters ($\sim
60$ percent in the whole cluster) than in the field ($\sim 40$ percent),
we expect there to be a larger proportion of red galaxies which could
potentially contaminate the blue galaxies due to photometric errors.
This would roughly double the contamination to be about 10 percent.

This is a conservative estimate of the contamination, because the
spectroscopic galaxy sample we use has a large incompleteness at the
blue end at redshifts beyond $0.2$, where SDSS targetted the luminous
red galaxy population. Thus we are missing a lot of the blue galaxy
population in the highest redshift bins in our spectroscopic sample.
Nevertheless we estimate what a roughly 10 percent contamination would
mean for the cross-correlation signal found for the blue galaxies.

@@

The null hypothesis that we would like to establish or rule out is
that the blue galaxies just consist of the infall population and show
no splashback feature. We assume a simple $r^{-1.5}$ power law for the
cross-correlation of the blue population with clusters consistent with
an infalling population, and the inferred 3d cross-correlation
function of the red galaxy population from our analysis.  Given these
cross-correlation functions we can estimate the cross-correlation of
the blue population when contaminated with a given amount of red
galaxies. We find that in order to reproduce the observed
cross-correlation function of blue galaxies, we need a contamination
of about 20\%. While our conservatively estimated contamination is
smaller than this value, a proper modeling of this contamination is
warranted before definitive conclusions can be drawn. Larger galaxy
surveys with better photometry such as the HSC or LSST would be of
significant help in alleviating these issues.

>>>>

\section{Estimating the contamination of the blue galaxy population}
\label{sec:Errors}

\begin{figure*}
    \includegraphics[width= \textwidth]{color_vs_z.pdf}
\caption{Scatter plot showing the $(g_{\mathrm{PS}}-r_{\mathrm{PS}})$ colors
of the matched galaxies versus their redshifts, where the red dots correspond
to galaxies identified as red from the SDSS spectroscopic colors and blue dots
correspond to galaxies identified as blue, respectively. The black, solid line
indicates the spline cut separating the two populations and excluding the red 
galaxies from the blue population at a confidence level of $3 \sigma$.}
   \label{fig:g-r_vs_z} 
\end{figure*}

To infer the color cut which separates star forming (blue) galaxies from the
quenched (red) galaxy population, we cross-matched the SDSS spectroscopic
sample to its Pan-STARRS photometry. In Figure~\ref{fig:g-r_vs_z}, we show the
plot of the Pan-STARRS $(g_{\mathrm{PS}}-r_{\mathrm{PS}})$ color as a 
function of redshift, and the color cut we use in our analysis. 
The SDSS spectroscopic sample is however quite shallow, 
and thus consists of galaxies that are brighter than the Pan-STARRS 
galaxies that we wish to cross-correlate. At fainter magnitudes, we can 
expect red galaxies to scatter into the blue population 
due to photometric errors, potentially contaminating the
correlation function measurement. This could erroneously cause the
splashback feature observed in the blue population. Therefore, we
need to assess the possiblity of such a contamination.

\begin{figure*}
    \includegraphics[width= \textwidth]{mag_errors.pdf}
\caption{Shown are the photometric errors of the Pan-STARRS galaxies versus
their magnitude in each of the used band. The dashed curves indicate the running
median of the photometric error.}
   \label{fig:mag_errors} 
\end{figure*}

In Figure~\ref{fig:mag_errors}, we show the photometric errors of the Pan-STARRS
galaxies as a function of magnitude in each of the bands we use. The
galaxies that we use in our cross-correlation analysis for the red/blue
galaxy population have an upper absolute magnitude limit of $M_{i}-5\log h=-18.94$. This
corresponds to a different apparent magnitude limit at each redshift.
For each spectroscopically matched galaxy, we figure out how faint the
apparent magnitude limit in the $i_{\mathrm{PS}}$ band is compared to the actual
apparent magnitude of the galaxy, recorded by Pan-STARRS. Aassume that the populations of
galaxies that we use to cross-correlate with clusters have the same
intrinsic colors, but are just fainter we infer the true
intrinsic magnitude of the galaxies that we cross-correlate in the
$g_{\mathrm{PS}}$ and the $r_{\mathrm{PS}}$ band. We randomly perturb these magnitudes 
by the expected photmometric errors at that magnitude as reported in Figure~\ref{fig:mag_errors}.

Next, we compute the fraction of galaxies which were intrinsically red
that now entered the blue population by the perturbation. Where we
defined the separation of the populations using the same color
cut. We find such a contamination of intrinsically red galaxies to
the blue population to be about 5 \%. This value would apply for a galaxy population
measured in the field. Given that the red fraction is higher in clusters ($\sim
60$ \% in the whole cluster) than in the field ($\sim 40$ \%),
we expect there to be a larger proportion of red galaxies which could
potentially contaminate the blue galaxies due to photometric errors.
This would roughly double the contamination to be about 10 \%.

This is a conservative estimate of the contamination, because the
spectroscopic galaxy sample we use has a large incompleteness at the
blue end at redshifts beyond $0.2$, where SDSS targetted the luminous
red galaxy population, recording only very few blue galaxies. 
Thus we are missing a lot of the blue galaxy
population in the highest redshift bins in our spectroscopic sample.
Nevertheless we estimate if a $\sim 10$ \% contamination could
cause the splashback signal found in the cross-correlation for the blue galaxies.

@@

The null hypothesis that we would like to establish or rule out is
that the blue galaxies just consist of the infall population and show
no splashback feature. We assume a simple $r^{-1.5}$ power law for the
3D cross-correlation of the blue population consistent for clusters with
an infalling population, and a 3D cross-correlation equal to the signal
found for the red galaxy population in our analysis. Given these
cross-correlation functions we can estimate the cross-correlation of
the blue population when contaminated with a given amount of red
galaxies, by considering a weighted sum of the two signals. 
We find that in order to reproduce the observed
cross-correlation function of the blue galaxies, we need a contamination
of about 20\%. While our conservatively estimated contamination is
smaller than this value, a proper modeling of this contamination is
warranted before definitive conclusions can be drawn. Larger galaxy
surveys with better photometry such as the HSC or LSST would be of
significant help in alleviating these issues.
